Methods for Polyphonic Music Transcription

### 2013-12-09 paper/paper.tex
Added comments about pictures to the paper
added section about error evaluation

@@

Polyphony means multiple simultaneous notes. Monophony means only a single note at a time. These terms carry slightly different meanings outside of the automated transcription field.

@@

\subsubsection{}

\subsubsection{Frame-level transcription error score}

\subsection{Method comparison}

>>>>

% Pictures to add to paper:
% spectrogram of single note
% spectrogram of multiple notes

% Show FFT vs. Constant q or log bins

% Show SVM output
% Show SVM with HMM output

% Show NMF output and NMF output with sparsity constraint
% Show NMF with Itakura-Saito Divergence

@@

Polyphony means multiple simultaneous notes. Monophony means only a single note at a time. These terms carry slightly different meanings outside of automated transcription research.

@@

We use a few metrics for evaluation, as per the existing literature.

\subsubsection{Overall accuracy}
$$Acc = \frac{TP}{TP+FP+FN} $$
where TP (true positives) is the number of correctly transcribed notes (over all notes), FP (false positives) is the number of unvoiced frames transcribed as voiced, and FN (false negatives) is the number of voiced frames transcribed as unvoiced.  Note that notes that are missed and notes that are inserted are weighed equally.
\subsection{Frame-level transcription error score}
In the previous measure "double counts" notes transcribed correctly but at the wrong time.  Frame-level transcription error score seeks to avoid that.
At each time frame, let $N_{sys}$ be the number of reported pitches, $N_{ref}$ the ground truth number of pitches, and $N_{corr}$, their intersection, is the number of correctly reported pitches.  Then we define 
$$E_{tot}=\frac{\sum_{t=1}^T \text{max}(N_{ref}(t),N_{sys}(t))-N_{corr}(t)}{\sum_{t=1}^T N_{ref}(t)}$$
$E_{tot}$ can be further split into three separate scores: $E_{sub}$, which counts the number (at each frame) of ground truth notes for which some other note was reported, $E_{miss}$, the number of ground truth notes which cannot be accounted for, and $E_{fa}$, the number of reported notes which cannot be paired with a ground truth note.  The equations for these, respectively, are 
$$E_{sub}=\frac{\sum_{t=1}^T \text{min}(N_{ref}(t),N_{sys}(t))-N_{corr}(t)}{\sum_{t=1}^T N_{ref}(t)}$$
$$E_{miss}=\frac{\sum_{t=1}^T \text{max}(0,N_{ref}(t))-N_{sys}(t)}{\sum_{t=1}^T N_{ref}(t)}$$
$$E_{fa}=\frac{\sum_{t=1}^T \text{max}(0,N_{sys}(t))-N_{ref}(t)}{\sum_{t=1}^T N_{ref}(t)}$$

\subsubsection{Note Onset Detection}
Frame-level transcription error requires a high level of precision.  An error-measure perhaps more fitting for this problem is note onset detection, since onset is usually more important than offset.  To be counted as correct, our transcribed note must be turned "on" within $100$ milliseconds of the ground truth onset.
\subsection{Method comparison}
